Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-25 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
sect 4

Figure \ref{fig:cdsr-reps} contains three of the five expressions defining the front of classroom \fw{Room3} which is pictured in the top of Figure~\ref{fig:rooms}. The boundary segments (shown in orange in Figure~\ref{fig:rooms}) define the extent of the region. \fw{(YMaxXFewestFn Room3)} and \fw{(YMinXFewestFn Room3)} are the points with the highest and lowest y coordinate out of the set of points within 5\% of the minimum x coordinate of \fw{Room3}. The next segment connect the lower left coordinate in the figure to the \fw{(YMinXFewestFn Group1)}, where \fw{Group1} includes the eight desks. There are two more boundary segments completing a polygon for this region. The semantic label \fw{FrontRegion} ties this polygon to a conceptual region, "the front of the room". This definition for the front of the room is specific to \fw{Room3} and its entities. It is clearly context-dependent because its extent is dependent on the arrangement of the anchor points used to define its boundary. If the desks were in a different position then the region would cover a different extent (e.g. if they were further to the left then the region would be smaller).

@@

We assume that a cognitive system will have a way of initially acquiring examples of CDSRs, e.g., by being taught through dialogue, sketching, or hand-coding. To avoid burdening potential users with the task of teaching the system every CDSR individually, it is desirable for a cognitive system to be able to automatically recognize similar regions after initial training. For example, after a janitorial robot has been taught where the front of one classroom is, it should be able to identify the fronts of other classrooms in the building. We have chosen \emph{analogy} as the approach our system will use to solve this problem, as analogy has been previously used to successfully combine semantic and geometric information in spatial reasoning tasks~\cite{Lockwood/etal2008}.

@@

We first create the base and target representations by running Dora in the two different classrooms. These are pictured in the top and bottom of Figure~\ref{fig:rooms} respectively. In each case, Dora is manually driven around the room to allow it to create a metric map. Once the map is created, Dora is then positioned such that the objects are observable and the visual recognition system is run. The map and object data that result from this are then passed on to the QSR generator. In the base case, Dora perceives 8 individual desks, a group entity containing these desks and the room area. To this we add the CDSR representing the front of the room. The case includes a total of 50 expression relating the 20 entities. Six of these expressions are used to define the boundary segments and CDSR representing the front of the room. The target case includes 26 expressions and 11 entities.

SME generates an analogy between the base and target cases enabling the transfer of the symbolic description of the front of the room to the new situation requiring \fw{Room3} and \fw{Group1} participate in the mapping as they are referenced by the anchor points in the base. The resulting analogy includes 26 correspondences between the entities and expressions and 32 candidate inferences. Four of these candidate inferences define the CDSR in the target with anchor points to the group of desks and the room in the target. The green region in the lower image of Figure \ref{fig:rooms} illustrates the transferred CDSR.

>>>>

Figure \ref{fig:cdsr-reps} contains three of the five expressions defining the front of classroom \fw{Room3} which is pictured in the top of Figure~\ref{fig:rooms}. The boundary segments (shown in orange in Figure~\ref{fig:rooms}) define the extent of the region. \fw{(YMaxXFewestFn Room3)} and \fw{(YMinXFewestFn Room3)} are the points with the highest and lowest y coordinate out of the set of points within 5\% of the minimum x coordinate of \fw{Room3}. The next segment connects the lower left coordinate in the figure to the \fw{(YMinXFewestFn Group1)}, where \fw{Group1} includes the eight desks. There are two more boundary segments completing a polygon for this region. The semantic label \fw{FrontRegion} ties this polygon to a conceptual region, ``the front of the room''. This definition for the front of the room is specific to \fw{Room3} and its entities. It is clearly context-dependent because its extent is dependent on the arrangement of the anchor points used to define its boundary. If the desks were in a different position then the region would cover a different extent (e.g. if they were further to the left then the region would be smaller).

@@

We assume that a cognitive system will have a way of initially acquiring examples of CDSRs, e.g., by being taught through dialogue, sketching, or hand-coding. To avoid burdening potential users with the task of teaching the system every CDSR individually, it is desirable for a cognitive system to be able to automatically recognize similar regions after initial training. For example, after a janitorial robot has been taught where the front of one classroom is, it should be able to identify the fronts of other classrooms in the building. Our system uses \emph{analogy} to solve this problem. We chose this approach because analogy has been previously used to successfully combine semantic and geometric information in spatial reasoning tasks~\cite{Lockwood/etal2008}.

@@

We first create the base and target representations by running Dora in the two different classrooms. In each case, Dora is manually driven around the room to allow it to create a metric map. Once the map is created, Dora is then positioned such that the objects are observable and the visual recognition system is run. The map and object data that result from this are then passed on to the QSR generator. The base and target maps are pictured in the top and bottom of Figure~\ref{fig:rooms} respectively. In the base case, Dora perceives 8 individual desks, a group entity containing these desks and the room area. To this we add the CDSR representing the front of the room. The case includes a total of 50 expression relating the 20 entities. Six of these expressions are used to define the boundary segments and CDSR representing the front of the room. The target case includes 26 expressions and 11 entities.

SME generates an analogy between the base and target cases enabling the transfer of the symbolic description of the front of the room to the new situation requiring \fw{Room3} and \fw{Group1} participate in the mapping as they are referenced by the anchor points in the base. The resulting analogy includes 26 correspondences between the entities and expressions and 32 candidate inferences. Four of these candidate inferences define the CDSR in the target with anchor points defined on the room and the group of desks in the target. The green region in the lower image of Figure \ref{fig:rooms} illustrates the transferred CDSR.
